\subsection{Appendix F - Additional Battlefields}
There are a few other types of battlefields created by fellow combatants.  Combatants wishing to try these need to either download them and run them locally, or find a server that runs them.

A few of the most popular appear below.

{\bf Capture the Flag - Attack/Defend (ctf\_*)}

Also called "Deposit the Flag." In this variant of capture the flag, the BLU team tries to sabotage the RED team's plans by planting a briefcase of fake intel in the RED base. The intel briefcase spawns near the BLU team and the BLU team must carry it into the red base and plant it in the intel rooms. The RED team tries to stop the BLU team from planting the briefcase until time runs out.

{\bf Dodgeball (db\_*)}

This custom game type pit two teams of all Pyros against each other. Homing rockets are launched from a central area of the map and the Pyros must use their Airblast to to reflect the projectiles at the opposing team.

{\bf Prop-hunt (ph\_*)}

In this custom game type, one team consists of nothing but Scouts disguised as random in-game props that cannot attack. The other team is made up of Pyros, and their objective is to hunt all the props down before the match ends. BLU loses health by attacking, although standing on the Control Point heals them.

{\bf Training Maps (tr\_*)}

Those combatants who wish to hone their skills in "safe" battlefields can do so using some of the many practice maps that are available.  The most popular practice map is “tr\_walkway” which needs to be downloaded.  See Appendix E: Map Installation on {{pageref}}.

{\bf Jump Maps (jump\_*)}

Jump maps are not actual maps, but rather courses where the players can practice their skills for jumping with the Soldier, Demoman and Scout. There is no actual combat going on in these maps.