\section{Combatant Presentation}
Combatants are expected to maintain decorum on the battlefield.  Combatants wishing to deviate from standardized dress may only do so by using headgear or medals awarded by the Administrator. Hats can be obtained via random drop, or through the crafting system. They serve no function other than the visual aesthetic, and to stand apart from those who do not have hats.

\subsection{Crafting}
Combatants dissatisfied with the item and weapon drops bestowed upon them by the Administrator may wish to recombine them to create weapons or headgear.  Crafting is accomplished through the main menu.  In order to successfully craft something, one must follow a recipe.  Recipes can be found online. Combatants should check for new recipies and keep up with the latest advancements in crafting technology, as some recipes and methods may become outdated over time. 

\subsection{Taunts}
The administrator encourages all classes to taunt each other in a menacing fashion. While the administrator remains indifferent to the outcome, combatants are encouraged to reward themselves for a job mildly well done by taunting their opponents. Generally, each weapon is provided with its own taunt. Combatants may find that a weapon's taunt can kill enemy combatants or themselves.
 
\subsection{Achievements}
The Administrator will recognize certain milestones by combatants, and in some cases, reward this achievement with new weapons. Combatants recognized by the Administrator in battle will have a trophy appear over their head. Achievements that have been earned and progress towards others can be seen by selecting "Achievements" at the main menu. Unattained Achievements can even be displayed on the HUD by checking the "Show on HUD" box in the Achievement screen.  Achievements are organized under 'General Achievements', which most classes can achieve, and Class specific achievements, which are only possible with the specified class, and usually relate to a special ability or weapon of that class.