\subsection{Appendix H - Glossary and Jargon}

{\bf Back Capping} Usually done by a Scout or a Spy, it’s when a player is able to sneak behind the enemy team and capture a point before the team can get back to stop him.

{\bf Bodyshot} A shot to the body instead of the head. Usually refers to a shot made by a Sniper. 

{\bf Buff} A property of a character or weapon being strengthened, such as an overheal from a Medigun or the mini-crit effect of the Soldier's Buff Banner.

{\bf Camping} While usually used in a derogatory way to refer to players who hide in one place waiting for an enemy, Team Fortress 2 includes many legitimate reasons to camp. Players should camp the point, the cart, and the intel room.

{\bf Capping} Capturing a point or moving the cart along its track.

{\bf Crocket} From the words 'Crit' and 'rocket'. Describes a rocket fired that has a critical hit boost. Crockets glow in color of the Soldiers' team.

{\bf Engie nest} Group of Engineers and their various buildings. Dislodging and breaking up Engie nests is vital to team, and by extension combatant, success. 

{\bf Facestab} The act of being stabbed in the front by a Spy which the game registers as a backstab. This is very frustrating to the victim because Butterfly Knife damage to anywhere other than the back shouldn't instantly kill. Usually caused by lag, although "legitimate" face stabs do still exist as a result of the collision boxes used for the Spy's backstab attack. 

{\bf Gib} Explode a player into chucks of flesh.

{\bf Highlander} A special competive gamemode. A highlander match consist of two teams with one of each class.

{\bf HUD} Heads Up Display. The display the user can see which shows attributes such as ammunition levels and health level.

{\bf Invuln} From the word 'invulnerable'. Describes how many Übercharges the Medic has used in a single life.  

{\bf Juggling} Bouncing an enemy in the air with either rockets, pipebombs/stickies or the Pyro's compression blast.

{\bf Killcam} The picture a combatant receives of their murderer after they die.
 
{\bf Meat shot} A point-blank Scattergun shot that deals over 100 damage.

{\bf Medic} chaining A tactic where two Medics equip the Medigun and Übersaws. Medic 1 Übers Medic 2, who then tries to land 4 hits with the Übersaw; if successful, Medic 2 can then Über Medic 1 and they trade positions.

{\bf Nerf} The act of a character, weapon, or property being weakened, usually as a result of balance issues. If a new weapon is released and found to be too powerful, it will be 'nerfed', weakening it to make it more balanced.

{\bf PUG} Stands for "Pick Up Game" where one or both teams start a match with a pre-determined set of rules

{\bf Pub Game/Server} From the word 'Public'. Describes playing in a public game or server, a game which is open to anyone, and is not a competition or a match that uses pre-set teams.

{\bf Rush/Class Rush} Describes the act of most of or an entire team switching to a single class and rushing out to the objective. Common rush classes include the Scout and Heavy. By doing this, the team tries to overwhelm the enemy team quickly and before they can react or muster counter classes. This is easily countered by a well organized team.

{\bf Spyro} A Spy disguised as a Pyro.

{\bf Spy Check} Act of checking for Spies. A Spy Check involves shooting or meleeing the surrounding area to see if a Spy is nearby.  Teammates especially should be fired upon to look for Spies in disguise.

{\bf Spy Crab} A graphical glitch which causes a Spy to walk similarly to a crab. It is achieved by equipping the disguise kit, looking into the sky, crouching and walking around. Etiquette states that a Spy Crab should never be harmed, whether friend or foe.

{\bf Stairstab} An advanced Spy tactic which involves a Spy on a staircase or slope, jumping over the head his opponent and getting a backstab.

{\bf Sticky Carpets} The act of placing stickies all over a given area, instead of concentrated in an area. This can work well if the stickies are spread out enough for the enemy team to not consider them a threat and walk into the carpet. This strategy is best done with the Scottish Resistance because of the ability to lay 14 stickies and selectively detonate them.

{\bf Telefrag} The death that occurs when a player stands on the exit side of a teleporter when an enemy uses the teleporter. The enemy will arrive at the exit and kill the player standing on the teleporter. Worth 1 kill to the Engineer. 

{\bf Turtling} An Engineer who has setup his nest in a choke point, and stays there. They are usually reinforced by other Engineers or teammates.

{\bf W+M1} A tactic used by the Pyro. It involves rushing forward with the Flamethrower with no plan except to light as many of the opposition on fire as possible.