\subsection{Heavy}
{\bf Bio}:
Like a hibernating bear, the Heavy appears to be a gentle giant. Also like a bear, confusing his deliberate, sleepy demeanor with gentleness will get you ripped limb from limb. Though he speaks simply and moves with an economy of energy that's often confused with napping, the Heavy isn't dumb, he's not your big friend, and he generally wishes you'd just shut up before he has to make you shut up.

{\bf Health}: 300

{\bf Purpose}
Suppression fire. Best in close quarters like hallways where enemies cannot run away, worst out in the open where Snipers can easily kill him.

\subsubsection {Weapons}


\begin {center}
\underline {Primary}
\end {center}

{\bf Minigun}: This minigun, whom the Heavy has named Sasha, has a high rate of fire, but takes a short period of time to "spin up" before it can be used. Holding the alt-fire key keeps this weapon spinning. While the gun is "spinning" the Heavy moves slower than he normally does, and if crouching as well as spinning, he cannot move.

{\bf Natascha*}: A minigun that causes 25\% less damage than Sasha, but slows the enemy on every hit.  Also stops a Demoman's Chargin' Targe.


\begin {center}
\underline {Secondary}
\end {center}

{\bf Shotgun}: Same as all other shotguns.

{\bf Sandvich*}: Using this lunchbox item will quickly recharge the Heavy's health to full.  However, the Heavy will be unable to attack or move while eating. Using the alternate fire key will throw the Sandvich onto the battlefield. Other combatants can pick the Sandvich up like a health pack, allowing the Heavy to keep his comerades alive. If the Heavy has thrown his Sandvich, he can get another one by picking up a health pack, or by using a resupply closet.

{\bf Dalokohs Bar**}: Eating this chocolate bar will make the Heavy's max health increase to 350 for 30 seconds. If eaten when below full health, it will also heal 120hp. Unlike the Sandvich, the Dalokohs Bar cannot be thrown on the battlefield.

\newpage

\begin {center}
\underline {Melee}
\end {center}

{\bf Fists}: The Heavy doesn't need a weapons, he uses his fists to punch enemies. Same as most other melee weapons.

{\bf Killing Gloves of Boxing (KGB)*}:  20\% slower fire rate than fists.  Killing an enemy with KGB grants the Heavy 5 seconds of critical hits for all weapons.


\subsubsection {Tactics}
\begin {itemize}

\item Heavies should try to stick close to a Medic buddy. A good Heavy/Medic combo can be devastating to the enemy team. 

\item If no Medics are nearby, a good Heavy knows when to break from combat and find a safe place to stop and have a Sandvich or knows where the health kits are on the map (See Maintaining Health on {{pageref}})

\item A Heavy can spin up his gun while he is in the air to save time and catch some enemies off guard.

\item A Heavy should keep in mind that his status as a huge, slow-moving damage sponge makes him a prime target for both Spies and Snipers. Heavies should remain aware of who is behind them, and should not engage enemy Snipers at long range.

\end {itemize}