\section{Introduction}
\label{Introduction}
This manual sets forth instructions to ensure uniformity and consistency among employees of Reliable Excavation Demolition (RED) and Builders League United (BLU) as determined by the Administrator/Announcer.  Uniformity and consistency are necessary steps towards ensuring that combatants are efficient in the execution of their duties on the battlefield. This manual is applicable to all combat classes.  Contained in this manual are:

 \begin{itemize}

\item General instructions that have been determined by the Administrator to be applicable to all combatants and are a requirement for all involved.
\item Descriptions of the different types of battlefields in which combat occurs.  
\item Instructions specified by the Administrator for specific combat classes.  Each combat class has mandated strengths and weaknesses and actions by combatants must maximize strengths while minimizing weaknesses.  
\item Team strategies.  Success on the battlefield will be determined by the combatants who display greater levels of teamwork.  As such, teamwork is vital for victory. 
\item Decorum guidelines.  While combatants are expected to be presentable at all times the Administrator recognizes that individualization is important. As combatant tenure grows, combatants may be awarded "headgear" which may be worn on the battlefield.
\end{itemize}
Combatants are expected to have this manual in their possession at all times. The Administrator has the authority to challenge any combatant's understanding of the information contained within. Inadequate understanding by the combatant will result in an unsatisfactory mark on your official combat record. Followed by death. Good luck!