\subsection{Medic}
{\bf Bio}:
What he lacks in compassion for the sick, respect for human dignity, and any sort of verifiable formal training in medicine, the Medic more than makes up for with a bottomless supply of giant needles and a trembling enthusiasm for plunging them into exposed flesh. Raised in Stuttgart, Germany during an era when the Hippocratic oath had been downgraded to an optional Hippocratic suggestion, the Medic considers healing a generally unintended side effect of satisfying his own morbid curiosity.

{\bf Health}: 150

{\bf Purpose}
The purpose of the Medic class is to provide mobile medical care to in-field combatants.  

\subsubsection {Weapons}

\begin {center}
\underline {Primary}
\end {center}

{\bf Syringe Gun}: Rapid fire pneumatic pistol that can launch damge-dealing syringes in an arc over moderate to long distances.  {{Medic annotation: that is not medicine!}}

{\bf Blutsauger*}: Another syringe firing device which heals three health per syringe that hits an enemy, but slows the Medic's natural health regeneration. 


\begin {center}
\underline {Secondary}
\end {center}

{\bf Medigun}: Heals teammates, and builds Übercharges. Deploy Übercharges for 8 seconds of complete invulnerability for the Medic and his patient. It takes about 40 seconds of constant healing to fully build a charge. The primary fire button is used to heal, while the alt fire button is used to deploy an Übercharge. For more information, see Übercharges on {{pageref}}. 

{\bf Kritzkrieg*}: Heals normally, and builds Kritz charges.  Kritz charges build faster than Übercharges.  For more information, see Übercharges on {{pageref}}.  Taunting with this weapon replenishes 10 health.


\begin {center}
\underline {Melee}
\end {center}

{\bf Bonesaw}: Used by the Medic to dice the bones of enemy combatants

{\bf Übersaw*}: This saw has a 20\% slower attack than its simple brother, but with each successful hit on an enemy player the Medic's Übercharge meter will go up by 25\% instantly. A successful taunt kill on an enemy with the Übersaw will add 50\%.

\subsubsection {Tactics}
\begin {itemize}
\item Medics are the only class that have regenerating health. The longer damage is avoided, the more quickly health regenerates, up to a maximum of 6hp/sec (4hp/sec if using the Blutsauger)

\item Medics can overheal teammates up to 150\% of their maximum health. This is a temporary effect and will gradually fade down to the maximum health, even if they take no damage. Since the overheal amount is based on percentage, classes with higher health (such as the Heavy or the Soldier) will gain more health, but it will also take more time to fully overheal them. While overhealing increases teammates' survivability significantly, healing wounded teammates still has higher priority than overhealing.

\item A successful Medic stays alive to build and deploy Übercharges, and to keep fellow combatants on the battlefield. A Medic should not be engaged in shooting someone as their primary weapon is fairly weak, but instead should focus on healing teammates and dodging enemy attacks.

\item Medics must keep moving to actively dodge enemy fire. They should also retreat earlier than other classes and keep in mind that staying alive is the top priority.

\item The "Medic auto-call" option, in the muitiplayer advanced options, is very useful. It makes it so whenever a teammate goes below a given percentage of their maximum health, an icon appears above their head and an audio alert sounds.

\item If a Medic heals for a good portion of the Setup time available on some battlefield types, they will be able to start the round with an Übercharge.

\item Good Medics are able to compensate for the slow firing and slight drop of their needles when using their primary weapon.

\item All Medics should keep in mind that they are a primary target for enemy combatants. Medics should strive to keep a high level of situational awareness in order to avoid a swift death.
\end {itemize}
{\bf HUD}: When using the Medigun or Kritzkrieg, the Heads-Up-Display will show a cross in the middle of the players' screen. When this is aimed at a friendly player, it will display the name and current health level of the player, allowing the Medic to discover who is low on health. The Übercharge meter of the weapon is also displayed on the HUD, as a percentage of full charge.
