\subsection{Pyro}
Bio
Only two things are known for sure about the mysterious Pyro: he sets things on fire and he doesn't speak. In fact, only the part about setting things on fire is undisputed. Some believe his occasional rasping wheeze may be an attempt to communicate through a mouth obstructed by a filter and attached to lungs ravaged by constant exposure to his asbestos lined suit. Either way, he's a fearsome, inscrutable on-fire Frankenstein of a man. If he even is a man.

Health: 175 HP

Purpose
Burn things, push people around, protect Engineers, locate Spies, ambush enemies.

Weapons
Primary
Flamethrower: Expels a cone of flames, which will ignite anyone on the opposing team within range. After someone is set on fire, the flames will deal 6 damage per second for 10 seconds, or until extinguished. The Flamethrower has an alternate attack: the compression blast (aka airblast). It expends 20 ammo and expels a cone of non-burning gas. The compression blast has a versatile array of important uses, see the tactics section.
Backburner*:  An alternative to the regular Flamethrower. This weapon causes 15\% more damage than the Flamethrower, but at a cost: it does not have airblasts. However, Pyros who successfully ambush the enemy by burning their backs will notice something:  All hits from behind are full critical hits, potentially causing an obscene amount of damage. 

Secondary
Shotgun: All Pyros should familiarize themselves with the shotgun. Lighting an enemy on fire and then finishing them off with the shotgun is a wholesome family pastime.
Flare Gun*: Shoots a long-range flare that deals hit damage and sets fire to an enemy. The flames will deal damage for 10 seconds, or until extinguished. If the flare strikes an enemy who is already on fire from short to medium range, the flare will be a mini-crit, doing 30\% more damage. If the flare hits an enemy who is already on fire from medium to long range, the flare will be a critical hit.

Melee
Fire Axe: The fire axe is a standard melee weapon.  There isn't anything special about it.  Frankly, this should only be used if no other melee weapons are available, or if melee is only used as a last resort when out of Flamethrower or Backburner ammo.
Axtinguisher*: Light someone on fire, and finish them off with this.  While it only does half damage to enemies who aren't on fire, it deals critical hits to those that are.  Combined with the Flamethrower or Flare Gun, this can be devastating. 
Homewrecker**: Deals 75\% of Fire axe damage against players, but deals 200\% damage against buildings.  It can also destroy an enemy Spy's sapper on friendly buildings with one hit.  This is the only weapon outside of the Engineer's wrench that can destroy sappers.


Tactics
Pyros are suited to close combat, so looking for ways to sneak around the enemy and come up behind their backs is important. Wait for enemies outside of exits and then ambush them.  
Pyros can also be be an enemy Spy's worst nightmare as the Pyro's flame will ignite an invisible or disguised enemy Spy, who can not then easily disappear.

Compression Blast
The compression blast is a versatile tool and can be used both offensively and defensively.

A well-timed compression blast can reflect rockets, grenades, stickies, baseballs, Jarate, flares, and even arrows! The reflected object changes team affiliation and gains mini-crits.

The compression blast can also be used to push opponents off cliffs, into various environmental hazards, or simply juggled in place. This can be used when an enemy team uses an Übercharge to either move the patient around or to separate the Medic from their patient. In addition, the compression blast can push people off a control point or away from a payload cart to stop the enemy from capturing or advancing.

If a teammate is on fire the compression blast can be used to put them out.