\subsection{Scout}
\label{Scout}
{\bf Bio}:
The youngest of eight boys from the south side of Boston, the Scout learned early how to problem solve with his fists. With seven older brothers on his side, fights tended to end before the runt of the litter could maneuver into punching distance, so the Scout trained himself to run. He ran everywhere, all the time, until he could beat his pack of mad dog siblings to the fray.

{\bf Health}: 125 HP

{\bf Purpose}:
Harass, capture objectives, steal intelligence.

\subsubsection {Weapons}

\begin {center}
\underline {Primary}
\end {center}

{\bf Scattergun}:  A double-barreled, lever-action, six-shot shotgun. Each blast has more power behind it than a standard shotgun, but also has a much wider spread, which quickly decreases it's effectiveness as distance increases.

{\bf Force-A-Nature*}: A double-barreled shotgun that knocks opponents backward when it hits them.  Opponents of a smaller stature are knocked back further, in accordance with Newton's laws.  The Scout can shoot it in midair to get an extra boost in the opposite direction.  For example, shooting down will propel him up. However, shooting twice does not propel the Scout twice as far. Like the Scattergun, the Force-A-Nature (or FAN, as it is often called) excels at close quarters combat.  It has a reduced clip size that only allows two shots that can be fired much faster than the scattergun, but will then need to be reloaded.


\begin {center}
\underline {Secondary}
\end {center}

{\bf Pistol}: Basic pistol, 12 shots per magazine, 48 rounds in total. Best used when the primary weapon is empty or the enemy is out of its range.

{\bf Bonk! Atomic Punch*}: Sometimes referred to as a "lunchbox item". Drinking this radioactive concoction will make the Scout immune to any and all damage for 6 seconds, including damage dealt by sentries. During this time the Scout may not attack, take the intelligence, capture points or push the cart. Additionally, the camera will switch from first to third person while under the effects of Bonk! Atomic Punch. After drinking it, there is a 15 second recharge time before he can take another drink.

{\bf Crit-a-Cola**}: Similar to the Bonk! Atomic Punch, Crit-a-Cola is a drink that replaces the Pistol.  Upon usage, the Scout is given mini-crits on all weapons for 6 seconds.  However, attackers will score mini-crits on the Scout for the duration of usage.

\newpage


\begin {center}
\underline {Melee}
\end {center}

{\bf Bat}: A light aluminum baseball bat. The fastest of all the melee weapons, but also one of the weakest.

{\bf Sandman*}: Wooden baseball bat complete with baseball. Hitting an enemy combatant with the baseball using the alternative fire button will stun them. The further the ball travels, the longer the enemy is stunned. If there's a ball rolling around on the ground, then the Scout can replenish his supply by picking it up. Having this bat equipped lowers the Scout’s maximum HP to 110. 

\subsubsection {Tactics}
\begin {itemize}
\item The biggest advantage Scouts have is their speed. They move significantly faster than every other class. This makes them much more agile, able to jump around their opponents and cause distractions.

\item A unique ability scouts have is known as the double jump.  This is the ability to jump while in the air, allowing them to change directions or jump higher.

\item Scouts can capture points at a rate twice as fast as other classes.  This means two scouts standing on a capture point will capture in half the time as two Soldiers, or a Medic and a Heavy.

\item Scouts have a low starting health, which means that they will need to be very aware of their health levels throughout the battle.  

\item An Engineer's Sentry Gun is the Scout's bane, but it isn't unbeatable. Scounts should listen for the beeps to know where it is and try to find an alternate path. Bonk! can be used that to get by or to quickly distract it for a teammate to destroy it.

\item Another way for scouts to effectively combat a Sentry Gun is firing at it with the pistol from outside of the sentry's range. The pistol is accurate enough to quickly take down a sentry, especially if it is unattended.
\end {itemize}