\subsection{Appendix G - Screenshots and Demo Recording}

Team Fortress 2 has the useful ability to record screenshots of the battle as well as record the entire battle for later playback.  The default screenshot key is `F5.'  Pressing this key will save an image of whatever is on the screen to an image in your TF directory inside of Steam.
\begin{lstlisting}
PC: 
Program Files\Steam\steamapps\<user name>\Team Fortress 2\tf\screenshots
\end{lstlisting}
\begin{lstlisting}
Mac: 
documents/Steam content/<username>/team fortress 2/tf/screenshots
\end{lstlisting}
Demos record combat for later playback.  They can be used to study one's own combat, or the combat of others.  To record a demo, simply type `record' into the console.  To name the demo, add it after the command.  Example:
\begin{lstlisting}
record shaningins
\end{lstlisting}
The command to stop recording is simple:
\begin{lstlisting}
stop
\end{lstlisting}
Demos are played back in a similar manner:
\begin{lstlisting}
playdemo <demoname>
\end{lstlisting}
And the command to stop playback:
\begin{lstlisting}
stopdemo
\end{lstlisting}

The interface for controlling playback can be displayed with the command:
\begin{lstlisting}
demoui2
\end{lstlisting}

Note:  Demos are often broken after updates.  That is, the software is unable to playback demos recorded by previous versions of the software.

Demo recordings are stored in the 'tf' directory:
\begin{lstlisting}
PC: 
Program Files\Steam\steamapps\<user name>\Team Fortress 2\tf\
\end{lstlisting}

\begin{lstlisting}
Mac: 
documents/Steam content/<username>/team fortress 2/tf/
\end{lstlisting}

There are many demos available of professional and highly skilled players that are available for study.  Demos are also a standard way of combating cheaters.  If a combatant is suspected of cheating, a demo recording of their behavior can be used to verify the accusation.

There are two types of demos: a player demo and a server demo.  A player demo is played back through the player's view.  A server demo is a recording of all players and the viewer is able to `fly' around the battlefield and view all actions.