\subsection{Sniper}
\label{Sniper}
{\bf Bio}:
In his former life as a tracker of dangerous game in the unforgiving Australian outback, the Sniper would spend months by himself. Prolonged isolation taught him a valuable lesson: You don't have to rely on other people if you never miss.

{\bf Health}: 125

{\bf Purpose}:
Eliminating high-value targets.

\subsubsection {Weapons}

\begin {center}
\underline {Primary}
\end {center}

{\bf Sniper Rifle}: A sniper uses the alt-fire button to zoom in with this rifle. The longer the rifle is zoomed in, the more damage a shot will do. Headshots deal critical hits, which do massive amounts of damage.

{\bf Huntsman*}: This bow and arrow is better suited for closer range. The fire button can be held to pull back the string and ready the arrow for release. Holding it for too long will cause the arrow to become wildly inaccurate. The arrow can be unnocked by clicking the alternate fire button. Headshots are critical hits.

\begin {center}
\underline {Secondary}
\end {center}

{\bf SMG}: Best used when enemies are too close to snipe, though ammunition is limited.

{\bf Jarate*}: Excrement based weapon. When thrown, Jarate will splash and soak nearby enemies. Any enemies covered in Jarate will take mini-crits for 10 seconds, unless they jump into water to wash it off. Jarate will also reveal cloaked spies that are in the splash radius. It also can be used to extinguish burning teammates. 

{\bf Razorback*}: The Razorback will block a single backstab from a Spy, and will not allow the Spy to attack for 2 seconds with his knife. After blocking the stab, the razorback will break, having no effect on subsequent backstabs.

\begin {center}
\underline {Melee}
\end {center}

{\bf Kukri}: The Kukri is a general melee weapon. Useful for when enemies are too close for comfort, or to deter spies.

{\bf Tribalman's Shiv**}: This knife causes opponents to bleed out for 8 seconds, but at a price. It causes over a third less damage than the Kukri.

\subsubsection {Tactics}
\begin {itemize}

\item The Sniper's main goal should be taking out the most valuable enemy targets. One tactic is to make sure that the opposing team's Medic is killed first, as this will keep the enemy from being healed, and can prevent an enemy Übercharge.

\item While using the Sniper Rifle, long range is best. If enemies advance too quickly to get long-distance shots, consider switching to the Huntsman.

\item Snipers should find a good vantage point from which to fire their Sniper Rile. This will give him an edge over his enemies but may make him an isolated target for a Spy.

\item Throwing Jarate on several enemies at once can stop a rush, or even turn the tide of the battle.

\item The Huntsman string can be pulled back while in mid-air, then released upon landing.

\item The Huntsman's arrow can be lit by a friendly Pyro. If an enemy is hit by this flaming arrow, they will burst into flames!
\end {itemize}

{\bf HUD}: When zoomed with the Sniper rifle, bars will appear on the screen. These bars reflect the relative damage a shot will inflict on an enemy, and will charge the longer the aim is held. If charged to full, a Sniper does substantial damage body shots (can kill weaker classes), or headshots that kill all classes, including an over-healed Heavy.