\subsection{Soldier}
\label{Soldier}
{\bf Bio}:
Though he wanted desperately to fight in World War 2, the Soldier was rejected from every branch of the U.S. military. Undaunted, he bought his own ticket to Europe. After arriving and finally locating Poland, the Soldier taught himself how to load and fire a variety of weapons before embarking on a Nazi killing spree for which he was awarded several medals that he designed and made himself. His rampage ended immediately upon hearing about the end of the war in 1949.

{\bf Health}: 200 HP

{\bf Purpose}:
Main assault class, shock and awe

\subsubsection {Weapons}

\begin {center}
\underline {Primary}
\end {center}

{\bf Rocket Launcher}: Projectile weapon that fires large, slow moving rockets that inflict large amounts of direct damage as well as splash damage. It can cause enemies to explode into piles of blood and body parts. 

{\bf Direct Hit*}: This launcher's rockets do 25\% more damage than the normal rocket launcher and move 80\% faster through the air, but have a much smaller blast radius (-70\%). It also does mini-crits when hitting opponents who have been launched into the air by an explosion.

\begin {center}
\underline {Secondary}
\end {center}

{\bf Shotgun}: This weapon is shared between the Soldier, Pyro, Heavy, and Engineer. Standard shotgun with 6 rounds, it is most effective at close range. 

{\bf Buff Banner*}: The Buff Banner can be used to rally a team.  When equipped, a "rage" meter appears on the HUD, filling up as damage is dealt.  Once the meter is full, the Soldier can activate it by blowing his bugle, and any teammates in the surronding area will shoot 100\% mini-crits for ten seconds.

{\bf Gunboats**}: Special boots, these provide a 75\% self damage reduction, enabling a Soldier to rocket jump to great heights with minimal damage to himself.

\newpage

\begin {center}
\underline {Melee}
\end {center}

{\bf Shovel}: Standard military issue folding entrenching tool. It works well for bludgeoning enemies. 

{\bf Equalizer*}: A pickaxe which gives increasing movement speed and damage bonuses with decreasing health. When the Equalizer is drawn, a Medic cannot heal or deploy an Übercharge on the Soldier.

{\bf Pain Train**}: Board with a railroad spike through it. Doubles capture speed when equipped. As such, it is only useful in game modes which involve capping points or pushing the cart. It increases combatant vulnerability to bullets by 10\%.

\subsubsection {Tactics}
\begin {itemize} 

\item Soldier have the ability to use their rockets to propel them to great heights.  In order to rocket jump, they shoot at their feet while simultaneously jumping. Jumping in this manner can enable Soldiers to reach areas inaccessible to other classes. Rocket jumping can be used to surprise enemy combatants and travel at higher speeds over the battlefield. While engaging the enemy, Soldiers can rocket jump and then rain rockets down on enemy combatants while in the air. Rocket jumping does cause the Soldier to damage himself, but it does so at a lower rate than damage to others. The Soldiers "Gunboats" unlockable weapon, which replaces the shotgun, allows the soldier to rocket jump without taking nearly as much damage.

\item Soldiers should fire their rockets at the feet of their opponents.  By firing at their feet instead of their body, the chance of causeing damage is increased, as the rocket will certainly explode once it hits the ground.  A rocket fired at the body of an opponent could miss, and not explode for a long distance, causing no damage at all.  Accurate shots will throw the opponent up in the air, who can then be juggled by firing additional rockets at the spot where they will land.  Another option the Soldier has is to switch to their shotgun and finish off their opponent with that weapon.

\item The Soldier is great at taking down sentries. Combatants can peek out from around a corner, fire a rocket, and retreat before an enemy sentry can taget them. Because rockets have a virtually unlimited range and Soldiers can also stand outside the range of enemy sentries to take them down. Firing at the walls or ground behind an enemy sentry is a good way to dislodge a stubborn Engineer. 

\item Some more advanced tactics for Soldiers include air shots (shooting enemies who are in the air with the rocket launcher), horizontal rocket jumping, crouch rocket jumping and effective use of the Equalizer.

\end {itemize}