\subsection{Spy}
{\bf Bio}:
He is a puzzle, wrapped in an enigma, shrouded in riddles, lovingly sprinkled with intrigue, express mailed to Mystery, Alaska, and LOOK OUT BEHIND YOU! But it is too late. You're dead. For he is the Spy — globetrotting rogue, lady killer (metaphorically) and mankiller (for real).

{\bf Health}: 125

{\bf Purpose}:
Countering Engineers and Snipers, picking off distracted players, reporting enemy positions from behind their lines.


\subsubsection {Weapons}

\begin {center}
\underline {Primary}
\end {center}

{\bf Revolver}: The revolver is the Spy's ranged weapon.

{\bf Ambassador*}: This weapon is another revolver, but with much more accuracy, a lower base damage, and slower firing rate.  Like the Sniper's rifle, headshots will result in critical hits.

\begin {center}
\underline {Secondary}
\end {center}

{\bf Electro-Sapper}: Solely used on enemy Engineer's buildings. Spies can place a sapper on any enemy building, without giving up their disguise or alerting enemy sentries. "Sapped" buildings are rendered inactive and if the sapper is not removed quickly, will be destroyed. Sappers can be removed by any Engineer, or Pyros equipping the Homewrecker melee weapon. The Spy can place an infinite number of sappers as fast as he wants. Spies cannot place sappers while cloaked.

\begin {center}
\underline {Melee}
\end {center}

{\bf Knife}: A melee weapon that requires true skill to employ, this blade normally does little damage, but is able to kill any opponent in one hit when used from behind.

\newpage

\begin {center}
\underline {PDA}
\end {center}

{\bf Disguise Kit}: Disguise is a vital asset to the master of espionage.  Using the Disguise Kit the Spy is able to disguise as any of the nine classes on either team. When they are disguised, they are mostly indistinguishable.  Spies appear to wear a paper mask to their fellow teammates. Firing a weapon will automatically remove any disguise, with the exception of the electro-sapper. A disguised Spy is able to fool enemy Engineer's buildings, allowing him to heal from dispensers and carts, take teleporters, and not be attacked by sentries.  Disguised spies can also be healed (and even Übered) by enemy Medics. However, when wearing a disguise, the spy will still receive damage from any enemy that may fire upon him, avoid this as it one of the only ways the enemy can tell you're a spy.

\begin {center}
\underline {Special}
\end {center}

{\bf Invisibility Watches}: Spies have the capability of becoming cloaking themselves, but there are a few things combatants should know before they start sneaking behind enemy lines. The watches are not perfect, they take a few moments to make the Spy completely invisable, and if the Spy bumps into an enemy while cloaked, he will be partly visable. There are three kinds of watches that a Spy can equip, each catering to a different play style:
\begin {itemize}
\item {\bf Invisibility Watch}: This watch can be replenished with metal, it will refill using any ammo source (See Maintaining Ammunition section on {{pageref}}), or it will recharge by not using it. It gives the Spy 9 second of full invisibility and it takes about 33 seconds to fully recharge by standing still, but in situations where metal is abundant this watch is a much needed asset to a Spy's arsenal.
\item {\bf Cloak and Dagger*}:This watch is motion based. It is the only watch of the three that can't be recharged with metal and ammo crates. This is because it only drains its charge when the Spy cloaked and moving. It can be recharged slowly by standing still while cloaked or by being uncloaked. By standing still, a Spy can be under the cloak indefinitely. 
\item {\bf Dead Ringer*}: This watch works differently than the other two. When pulling this watch out, the Spy will not automatically cloak. Instead, the next damage the Spy takes will cause the watch to simultaneously activate cloaking and drop a fake body for the other team to see, feigning a death. It also negates 90\% of the damage that would be taken while cloaked. Be warned though, this watch has a short cloak time and makes a loud noise when uncloaked, drawing others' attention.
\end {itemize}

\newpage

\subsubsection{Tactics}
\begin {itemize}
\item Cloak and Dagger:  This watch has a habit of promoting camping, because combatants can stay still in one spot for indefinite periods of time, hidden and waiting for kills.  A good Spy is always moving, and always has a new sentry to sap or Heavy to backstab.

\item Dead Ringer: Because of the short cloak range and noise made upon decloaking, care should be made to find a inconspicuous place to decloak, away from alert ears and prying eyes.  Even if out of sight, the Dead Ringer's sound will alert the enemy to the presence of a Spy nearby, and lead to an increase in counter-Spy measures such as Spy Checking and overall alertness.

\item Spies should move towards their targets indirectly.  A spy heading straight for an engie nest is sure to arouse suspicions, but if it looks like their attention is off somewhere else, they will seem more safe.

\item Teammates should shoot at disguised spies to increase their authenticity.  
\end {itemize}