\section{Team Strategy}
\label{Team_Strategy}
All combatants need to realize that they are a team and that they must look out for each other. Teams that fail to do this wind up dead. There's a reason the game is called "Team" Fortress.

Protect Medics as they are going to be targeted by the other team. A team without a Medic is easier to destroy, so make their defense a priority.

\subsection{Communication Guidelines}
A good team communicates well. Note that some players will have microphones while others will not - a combatant that does not have a microphone should use their voice menu commands to the best of their capacity. A good example of this would be having potential Über targets call out "Medic" when they want an Übercharge to be activated. Call out sentry positions, Spies, and unexpected enemy tactics.  Combatants can let the Medic know when they are ready to receive an Übercharge, or need healing. Be aware of the presence of Spies and call out their position and disguise, if possible. But try to pay attention to teammates -- if they need healing too, and the Medic is working through them, be patient and don't keep pressing the key (by default, "e") that calls the doctor (it gets annoying for the Medic).  Also, be aware that while some servers have Team-Talk on, meaning only teammates can hear and speak to each other, others use All-Talk, meaning all players can communicate with each other regardless of team.  If playing on an All-Talk server, it might be wise to refrain from giving out too much information, as it could aid the other team in forming appropriate countermeasures.  Especially tricky combatants could use All-Talk to their advantage by giving out false information.
"You are trying my patience!" ~Medic

\subsection{Engineer-related Etiquette}
Upgrade the Engineer's buildings.  During the setup phase all players, except for Medics, should consider switching to Engineer and helping them build their buildings. If they are far away from spawn, combatants can help an Engineer by upgrading his building until they are out of metal, then kill
themselves so that the Engineer can collect an additional 100 metal from their dropped weapons. (A player can suicide by typing explode into the console)

Teleporter Queuing.  If two combatants reach the teleporter at the same time, they shouldn't waste time fighting over it. It is common courtesy to let Engineers (to keep thier buildings alive) and Medics (to keep people on the front lines alive) go before you. After Engineers and Medics, slower classes benefit more from using teleporters. Scouts should rarely use teleporters because they can run to the front lines very quickly without it.

Engineers should place teleporter entrances immediately outside of the spawn point. 

Teammates should try to protect the Engineer's sentries, teleporters, and dispenser.

\subsection{Other Information}
Medics are a neccessary component of a successful team. If a team is having a difficult time progressing, a Medic should prioritize building up an Übercharge to break through a strong defensive opposition. (see the section on Übercharge in General Instructions page \pageref{Ubercharge}).

Spies are generally disguised as members of their opposing team. Using a weapon on an enemy Spy will cause damage, while using a weapon on a teammate will not. For this reason it is highly recommended that players 'Spy-check' any 'teammate' they suspect may be a Spy by firing their weapons at him. Teammates can let each other know they are not a Spy by taunting, firing their weapons, switching weapons, or using their microphone. Friendly teammates cannot collide with players on their own team, and will instead walk through them. However, they can collide with enemy spies disguised as members of their team. Thusly it is advised that they attempt to walk through everyone.

If needed,players should take the time to 'regroup' and re-form. Although it sacrifices time and possibly ground to the enemy, it allows the players to focus and work together as a team again.