\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{parskip}
\pagestyle{headings}
\title{The Missing Team Fortress 2 Manual}
\date{}
\begin{document}

\maketitle
\newpage
\tableofcontents


\newpage
\section{Introduction}
  \label{Introduction}
This manual sets forth instructions to insure uniformity and consistency among employees of Reliable Excavation Demolition [RED] and Builders League United [BLU] as determined by the Administrator/Announcer.  Uniformity and consistency is a necessary step towards insuring that combatants are efficient in the execution of their duties on the battlefield. This  manual is applicable to all combat classes.  Contained in this manual:

  \begin{itemize}

\item  General instructions that have been determined by the Administrator to be applicable to all combatants and are a requirement for all involved.

\item  Descriptions of the different types of battlefields in which combat occurs.

\item  Instructions specified by the Administrator for specific combat classes.  Each combat class has mandated strengths and weaknesses and actions by combatants must maximize strengths while minimizing weaknesses.

\item  Success on the battlefield will be determined by the combatants which display greater  levels of teamwork.  As such, teamwork is vital for victory. The Administrator mandates behaviours that encourage teamwork and punishment for deviation from these is death.

\item  While combatants are  expected to be presentable at all times the Adminstrator recognizes that  individualization is important.  As combatant tenure grows, combatants  may be awarded "headgear" which may be worn on the battlefield.
\end{itemize}

Combatants are expected to have this manual in their possession at all times. The Administrator has the authority to challenge any combatant's understanding of the information contained within. Inadequate understanding by the combatant will result in death.


\newpage
\section{General Instructions}
\label{general_instructions}

These Instruction have been determined by the Administrator to be applicable to all combatants and are a requirement for all involved. Section \ref{Introduction}

  \subsection{Keyboard Controls}
  Combatants have a standardized way for controlling conduct on the battlefield:

\begin{table}[h!b!p!]
\caption{Common Actions}
\begin{tabular}{|c|l|}
  \hline
  Key & Action\\
  \hline
  \texttt{w}&Move Forward\\
  \texttt{a}&Strafe Left\\
  \texttt{d}&Strafe Right\\
  \texttt{s}&Move Backward\\
  \texttt{Space}&Jump\\
  \texttt{Ctrl}&Crouch\\
  \hline
\end{tabular}
\label{table_common_actions}
\end{table}

\end{document}